---
title: "COVID SL FLEXDASHBOARD"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

HOME {data-orientation=columns}
=====================================
Column {data-width=800}
-------------------------------------
### FT plot
```{r}
```
Column {data-width=200}
-------------------------------------
### Key facts
```{r}
```
TIME SERIES{data-navmenu=SL1}
=====================================
Row{data-height=800 .tabset}
-------------------------------------
### NATIONAL
```{r}
```
### REGIONAL
```{r}
```

Row{data-height=200}
-------------------------------------
### Description of measures

```{r}
```
MAPS{data-navmenu=SL1}
=====================================
Row{data-height=800}
-------------------------------------
### PLOTS
```{r}
```
Row{data-height=800}
-------------------------------------
### Description of measures
```{r}
```
ALL DATA{data-navmenu=SL1}
======================================
### KABLE FOR DATA DOWNLOAD
```{r}
```
TIME SERIES{data-navmenu=SL2}
=====================================
Row{data-height=800 .tabset}
-------------------------------------
### NATIONAL
```{r}
```

### REGIONAL
```{r}
```


Row{data-height=200}
-------------------------------------
### Description of measures

```{r}
```

MAPS{data-navmenu=SL2}
=====================================
Row{data-height=800}
-------------------------------------
### PLOTS
```{r}
```
Row{data-height=800}
-------------------------------------
### Description of measures
```{r}
```
ALL DATA{data-navmenu=SL2}
======================================
### KABLE FOR DATA DOWNLOAD
```{r}
```
AGGREGATION
=====================================
### Still coming soon
