---
params:
    set_title: "x"
    set_subtitle: "y"
    set_author: "a"
title: "`r params$set_title`"
subtitle: "`r params$set_subtitle`"
author: "`r params$author`"
output: 
  html_document
---


```{r, include=FALSE, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE)
```

# {.tabset}
***
## Motivation

Economic coping with COVID-19 shutdown measures directly influence households’ ability to comply with public health policies such as social distancing, which may be especially challenging in a refugee setting. Researchers will collect phone survey data from participants of a USAID-funded Graduation study with refugees and neighboring communities of the Kamwenge refugee settlement in Western Uganda. The on-going study tests how Graduation-style interventions can help participants in a post-conflict setting of a refugee settlement improve food and nutrition security and self-reliance. The additional data in the context of COVID-19 will allow us to document to what extent the interventions help participants cope with extreme economy-wide shocks. We will also partner with local organizations to include survey questions that will be used directly to inform their local policy response to the pandemic.

## Team

* Lasse Brune

* Nathanael Goldberg 

* Dean Karlan 

* Doug Parkerson

* Chris Udry


## How To

This dashboard presents results from the most recent surveys available. Click on each section to see results. The “Aggregates” tab presents results graphically the “Definitions of measures” tab shows the exact question wording and answer categories.

To download data or search for an indicator, select the “All data” tab. Data can be downloaded as a csv or Excel file.

For comments or questions on the dashboard, please email Julio Solís at  julio.solis@wzb.eu.

***

```{r, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
k  <- 1
```


#   {.tabset .tabset-pills}

<!-- Optionally add FT style plots -->

```{r, child = ftplotRmd, echo = FALSE, eval = ft_plot}

```

```{r, child = childRmd, echo = FALSE, eval = k>0}

```


## All Data  {.tabset  .tabset-pills}

`r my_args$data_note`

### Browse data  {.tabset}

```{r datatable, echo = FALSE, message = FALSE, warning = FALSE}

  my_data %>%
  datatable(rownames = TRUE, 
            extensions = c('Buttons', 'Scroller', 'ColReorder', 'FixedColumns'), 
            options = list(colreorder = TRUE, 
                           dom = 'Bfrtip',
                           buttons = c('copy', 'csv', 'excel'),
                           deferRender = TRUE,
                           scrollY = 200,
                           scroller = TRUE,
                           scrollX = TRUE
                           #          fixedColumns = list(leftColumns = 1)
            )) 

```

